---
title: "Clearance calculations"
author: "Zen Tamura"
date: 2021-09-07
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_chunk$set(error = FALSE)
# knitr::opts_chunk$set(message = FALSE)
# knitr::opts_chunk$set(warning = FALSE)

##########
knitr::opts_chunk$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
##########
```

```{r}
sessionInfo()
```


```{r}
library(tidyverse)
```


# 1. Load data

```{r}
# urine creatinine concentration in mg/dL
urine_creatinine_concentration <- read_csv("data/creatinine_concentration.csv", 
                                           skip = 1,
                                           locale = locale(encoding = "UTF-8"))
urine_creatinine_concentration

# urine flow rate in mL/min
urine_flow_rate <- read_csv("data/urine_flow_rate.csv", 
                            skip = 1,
                            locale = locale(encoding = "UTF-8"))
urine_flow_rate

# osmotic pressure in mOSM/kg/H2O
osmotic_pressure <- read_csv("data/osmotic_pressure.csv", 
                            skip = 1,
                            locale = locale(encoding = "UTF-8"))
osmotic_pressure

# pH
ph <- read_csv("data/ph.csv", 
               skip = 1,
               locale = locale(encoding = "UTF-8"))
ph

# ammonia concentration in g/L
ammonia_concentration <- read_csv("data/ammonia_concentration.csv", 
                                  skip = 1,
                                  locale = locale(encoding = "UTF-8"))
ammonia_concentration
```

# 2. Creatinine clearance

$$C_{\text{creatinine}} = \frac{[U]_{\text{creatinine}} \cdot \dot{V}}{[P]_{\text{creatinine}}}$$

where
$[U]_{\text{creatinine}}$: urine concentration of creatinine (mg/dL)
$\dot{V}$: urine flow rate (mL/min)
$[P]_{\text{creatinine}} = 1.15$ mg/dL : plasma concentration of creatinine (mg/dL)

```{r}
creatinine_clearance <- urine_creatinine_concentration[,2:6] * urine_flow_rate[,2:6]
creatinine_clearance <- creatinine_clearance / 1.15


# creatinine_clearance %>% 
#     add_column(groups = urine_creatinine_concentration$`班/時間(min)`, .before = 1) %>% 
    # write_csv("result/creatinine_clearance.csv")

creatinine_clearance <- add_column(creatinine_clearance,
                                   groups =  urine_creatinine_concentration$`班/時間(min)`,
                                   .before = 1)

creatinine_clearance
# add_column(creatinine_clearance, groups = urine_creatinine_concentration$`班/時間(min)`, .before = 1)

# creatinine_clearance <- cbind(rn = rownames(urine_creatinine_concentration),
#                               creatinine_clearance,
#                               row.names = NULL)
# creatinine_clearance$groups <- urine_creatinine_concentration[,1]
# write_csv(creatinine_clearance, "result/creatinine_clearance.csv")

# creatinine_clearance %>% 
#     rename(groups = `班/時間(min)` ) %>% 
#     write_csv("result/creatinine_clearance.csv")

# write_csv(creatinine_clearance, "result/creatinine_clearance.csv")

```


# 3. Clearance of osmoles (浸透圧クリアランス)

clearance in mL/min

$$C_{\text{osm}} = \frac{[U]_{\text{osm}} \cdot \dot{V}}{[P]_{\text{osm}}}$$

where,

$[U]_{\text{osm}}$: urine osmolarity (mOsm / (kg H2O))
$\dot{V}$: urine flow rate (mL/min)
$[P]_{\text{osm}} = 290$ (mOsm / (kg H2O)): plasma osmolarity

```{r}
osmoles_clearance <- osmotic_pressure[, 2:6] * urine_flow_rate[, 2:6]
osmoles_clearance <- osmoles_clearance / 290
# osmoles_clearance %>% 
#     add_column(groups = osmotic_pressure$`班/時間(min)`, .before = 1) %>% 
    # write_csv("result/osmoles_clearance.csv")
osmoles_clearance <- add_column(osmoles_clearance, groups = osmotic_pressure$`班/時間(min)`, .before = 1)
osmoles_clearance
```


# 4. Free water clearance

$$C_{\text{H2O}} = \dot{V} - C_{\text{osm}} $$
where
$C_{\text{osm}}$: clearance of osmoles

```{r}
free_water_clearance <- urine_flow_rate[, 2:6] - osmoles_clearance[, 2:6]
free_water_clearance <- add_column(free_water_clearance, 
                                   groups = osmotic_pressure$`班/時間(min)`,
                                   .before = 1)
# write_csv(free_water_clearance, "result/free_water_clearance.csv")
free_water_clearance
```

# 5. Reabsorption rate

If the filtered volume = water's volume, then reabsorption rate (mL/min) is

$$\text{Reabsorption rate} = \text{GFR} -  \dot{V} \approx C_{\text{creatinine}} - \dot{V}$$

```{r}
# creatinine_clearance
reabsorptiona_rate<- (creatinine_clearance[, 2:6] - urine_flow_rate[, 2:6]) * 100 / creatinine_clearance[, 2:6]
reabsorptiona_rate <- add_column(reabsorptiona_rate,
                                 groups = urine_flow_rate$`班/時間(min)`,
                                 .before = 1)
# write_csv(reabsorptiona_rate, "result/reabsorption_rate_210918.csv")
reabsorptiona_rate
```



